
---
title: "RD Robustness Project"
author: "Maor Milgrom"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    df_print: paged
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, fig.height=4.5, root.dir = 'C:/Users/yaela/Dropbox (Brown)/Brown/RA/RD/R')
setwd("C:/Users/yaela/Dropbox (Brown)/Brown/RA/RD/R")  
```


# Introduction
The goal of this project is to test the robustness of the Regression-Discontinuity analysis to different extreme cases, via simulations, using the 'rdrobust' package.  



## This Document: Excercise \#1
Replacing observations outside Optimal Bandwitdh (OBW) with zeros, or dropping them.    

### Select exercise type:
```{r select_exercise}
exercise="bwo"      # Type of exercise - "zero" or "bwo" ('bandwidth only')
```


```{r subtitle, include=F}
subtitle_var = ifelse(exercise=="zero", "Replace with zeros", "Drop outside OBW")
```

---
subtitle: "Exercise: `r subtitle_var`"
<!-- knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding=encoding, output_file='new_file_name.pdf') }) -->
---


```{r packages, include=F}
library(dplyr)
library(rdrobust)
library(ggplot2)
library(reshape2)
library(knitr)
set.seed(1)
```



### Set Parameters
Here we set the main parameters for the excercise:

```{r parameters}
jump=10           # Size of jump at cutoff
loop=1000
figs.iter.save=5
quadratic=T       # T - quadratic DGP, F - linear
symm_obw="mserd"  # mserd - symmetric OBW, msetwo - asymmetric OBW 
normal.x=T        # T - normal draws of x around cutoff, F - uniform draws
dgp.sd=10         # sd of normal noise added to DGP
bc=F              # bias-corrected estimates or conventional
```


```{r setup, include=F}
### dataframes for storing results
results<- as.data.frame(matrix(0, ncol = 4, nrow = loop))
colnames(results) <- c("coef","obw","obw_l","obw_r")
results.exercise<- as.data.frame(matrix(0, ncol = 6, nrow = loop))
colnames(results.exercise) <- c("coef","obw","obw_l","obw_r",
                             "coef_diff","obw_diff")

### Extensions for files based on parameters selected
figs.dir="C:/Users/yaela/Dropbox (Brown)/Brown/RA/RD/R/figures/"
quad_test=ifelse(quadratic==T,"quadratic","linear")
normal_test=ifelse(normal.x==T,"rnorm","runif")
bc_test=ifelse(bc==T,"bc","c")
save.ext=paste(bc_test,quad_test,normal_test,sep = "_")
file.var=paste("summary_",save.ext,".html",sep = "")
begin.figures=loop-figs.iter.save
```


### Simulate DGP + Plot
```{r dgp}
## dataframe for dgp
df <- as.data.frame(matrix(0, ncol = 0, nrow = length(seq(-100,100,0.01))))
df$x=round(seq(-100,100,0.01), digits=2)
df=subset(df,df$x!=0)
df$treated <- ifelse(df$x>0, 1, 0)

df$y.model<- 0.5*df$x  - 0.025*df$x^2*quadratic + jump*df$treated
df$y=df$y.model+rnorm(length(df$x),0,dgp.sd)

## dataframe for draws (samples)
sample.x <- as.data.frame(matrix(0, ncol = 0, nrow = nrow(df)/10)) 
```

```{r plot_dgp, echo=F}
### Plot DGP
df %>%
  filter(x > -50 & x < 50) %T>%
  plot(y~x,., ylim = range(c(y,y.model)),
       col="blue", ylab = "Y", xlab = "X") %T>%
  par(new = T) %>%
  plot(y.model~x,., ylim = range(c(y,y.model)),
       axes = FALSE, xlab = "", ylab = "")
  title(main = "DGP + Model")
```


```{r dgp_plot_save, include=FALSE}
figure_name=paste(figs.dir,"dgp_",quad_test,".png",sep = "")
png(figure_name)
df %T>%
  plot(y~x,., ylim = range(c(y,y.model)),
       col="blue", ylab = "Y", xlab = "X") %T>%
  par(new = T) %>%
  plot(y.model~x,., ylim = range(c(y,y.model)),
       axes = FALSE, xlab = "", ylab = "")
dev.off()
```

### Iterations
Running `r loop` iterations, and saving figures from `r figs.iter.save` last iterations to file.
In each iteration, we: \newline

1. draw randomly `r nrow(df)/10` observations around the cutoff.
2. compute the OBW and RD coefficient.
3. drop observations outside OBW/replace them with zero
4. compute again the OBW and RD coefficient.

```{r iterations, include=F}
for(i in 1:loop) {
  if (normal.x==T) {
    sample.x$x <- round(rnorm(nrow(df)/10, 0, 10),digits = 2) 
  } else {
    sample.x$x <- round(runif(nrow(df)/10, -20,20),digits = 2) 
  }
  
  sample.x=subset(sample.x, x>-100 & x<100)
  sample=as.data.frame(inner_join(df, sample.x, by="x"))
  results.current=rdrobust(sample$y,sample$x,bwselect = symm_obw)
  results[i,1]=results.current$coef[bc+1]-jump # normalizing to zero
  results[i,3:4]=results.current$bws[bc+1,1:2]
  results[i,2]=results[i,3]+results[i,4]
  

  if (exercise=="zero") {
    sample.exercise=sample
    sample.exercise$y <- ifelse(sample$x> -results[i,3] & 
                                     sample$x< results[i,4], sample$y, 0)
    
  } else if (exercise=="bwo") {
    sample.exercise=subset(sample,x> -results[i,3] & x< results[i,4])
  }
  
  results.current=rdrobust(sample.exercise$y,sample.exercise$x,bwselect = symm_obw)
  results.exercise[i,1]=results.current$coef[bc+1]-jump # normalizing to zero
  results.exercise[i,3:4]=results.current$bws[bc+1,1:2]
  results.exercise[i,2]=results.exercise[i,3]+results.exercise[i,4]
  
  results.exercise[i,5:6]=results[i,1:2]-results.exercise[i,1:2] # computing diff from base

### FIGURES INSIDE LOOP - SPECIFIC DRAWS ###
if (i >= begin.figures) {
    coef_base=paste("Base: Coef = ",round(results[i,1],digits = 2)+jump,sep = "")
    coef_treat=paste(exercise,": Coef = ",round(results.exercise[i,1],digits = 2)+jump,sep = "")
    
    figure_name=paste(figs.dir,"sample",i,exercise,"_",save.ext,"_","model.png",sep = "")
    png(figure_name)
    temp.exercise=sample.exercise %>%
      filter(x > -20 & x < 20)
    temp=sample %>%
      filter(x > -20 & x < 20)
    plot(temp$y~temp$x, ylim = range(c(temp.exercise$y,temp$y)),
         xlim = range(c(temp.exercise$x,temp$x)),
         col="red", ylab = "Y", xlab = "X")
    par(new = T)
    plot(temp.exercise$y~temp.exercise$x, ylim = range(c(temp.exercise$y,temp$y)),
         xlim = range(c(temp.exercise$x,temp$x)),
         col="blue", ylab = "Y", xlab = "X")
    par(new = T)
    plot(temp$y.model~temp$x, ylim = range(c(temp.exercise$y,temp$y)),
         xlim = range(c(temp.exercise$x,temp$x)),
         col="black", ylab = "Y", xlab = "X")
    abline(v = c(-results[i,3], -results.exercise[i,3],
                 results[i,4], results.exercise[i,4]),
           col=c("blue","red", "blue", "red"),
           lty=c(1,2,1,2), lwd=c(1,2,1,2))
    legend("top", legend=c(coef_base, coef_treat),
           col=c("blue", "red"), lty=1:2, cex=0.8)
    dev.off()
    
    
    figure_name=paste(figs.dir,"rd_plot",i,"_",save.ext,".png",sep = "")
    png(figure_name)
    rdplot(sample$y,sample$x)
    dev.off()
    
    
    figure_name=paste(figs.dir,"sample",i,"_",save.ext,".png",sep = "")
    png(figure_name)
    sample %>%
      filter(x > -30 & x < 30) %T>%
      plot(y~x,., ylim = range(c(y,y.model)),
           col="blue", ylab = "Y", xlab = "X") %T>%
      par(new = T) %>%
      plot(y.model~x,., ylim = range(c(y,y.model)),
           axes = FALSE, xlab = "", ylab = "")
    dev.off()
  }
}
```


### Presenting figures from last iteration for illustration

```{r sample_figures_present, echo=F}
    i=loop
    coef_base=paste("Base: Coef = ",round(results[i,1],digits = 2)+jump,sep = "")
    coef_treat=paste(exercise,": Coef = ",round(results.exercise[i,1],digits = 2)+jump,sep = "")
    
      sample %>%
      filter(x > -30 & x < 30) %T>%
      plot(y~x,., ylim = range(c(y,y.model)),
           col="blue", ylab = "Y", xlab = "X") %T>%
      par(new = T) %>%
      plot(y.model~x,., ylim = range(c(y,y.model)),
           axes = FALSE, xlab = "", ylab = "")
      title(main = "Draw from DGP + Model")
    
    rdplot(sample$y,sample$x, title = "RD Plot for basline")

    temp.exercise=sample.exercise %>%
      filter(x > -20 & x < 20)
    temp=sample %>%
      filter(x > -20 & x < 20)
    plot(temp$y~temp$x, ylim = range(c(temp.exercise$y,temp$y)),
         xlim = range(c(temp.exercise$x,temp$x)),
         col="red", ylab = "Y", xlab = "X")
    par(new = T)
    plot(temp.exercise$y~temp.exercise$x, ylim = range(c(temp.exercise$y,temp$y)),
         xlim = range(c(temp.exercise$x,temp$x)),
         col="blue", ylab = "Y", xlab = "X")
    par(new = T)
    plot(temp$y.model~temp$x, ylim = range(c(temp.exercise$y,temp$y)),
         xlim = range(c(temp.exercise$x,temp$x)),
         col="black", ylab = "Y", xlab = "X")
    abline(v = c(-results[i,3], -results.exercise[i,3],
                 results[i,4], results.exercise[i,4]),
           col=c("blue","red", "blue", "red"),
           lty=c(1,2,1,2), lwd=c(1,2,1,2))
    legend("topleft", legend=c(coef_base, coef_treat),
           col=c("blue", "red"), lty=1:2, cex=0.8)
    title(main = paste0("Comparing baseline to ",exercise))
    
    rdplot(sample.exercise$y,sample.exercise$x, title = paste0("RD Plot for ",exercise))
```

## Results

### Figures summarizing iterations
```{r figures_summary_print, echo=F, fig.height=3}

## PDF'S OF LEVELS
ggplot(results, aes(coef)) +  stat_density(geom="line") + 
  geom_vline(aes(xintercept=0), colour="#BB0000", linetype="dashed") +
  ggtitle("Density of RD coefficients: basline")

ggplot(results.exercise, aes(coef)) + stat_density(geom="line") +
  geom_vline(aes(xintercept=0), colour="#BB0000", linetype="dashed") +
    ggtitle(paste0("Density of RD coefficients: ",exercise))


## treat_base_diff
ggplot(results.exercise, aes(coef_diff)) + stat_ecdf(geom = "step") +
      ggtitle(paste0("CDF of difference b/w coefficients of baseline and ",exercise))


ggplot(results.exercise, aes(obw_diff)) + stat_ecdf(geom = "step") +
        ggtitle(paste0("CDF of difference b/w OBW of baseline and ",exercise))
```

```{r figures_summary_save, include=F}

## PDF'S OF LEVELS
figure_name=paste(figs.dir,"coef","_",save.ext,".png",sep = "")
png(figure_name)
ggplot(results, aes(coef)) + stat_density(geom="line") + 
  geom_vline(aes(xintercept=0), colour="#BB0000", linetype="dashed")
dev.off()


figure_name=paste(figs.dir,"coef","_",exercise,"_",save.ext,".png",sep = "")
png(figure_name)
ggplot(results.exercise, aes(coef)) + stat_density(geom="line") +
  geom_vline(aes(xintercept=0), colour="#BB0000", linetype="dashed")
dev.off()


### treat_base_diff
figure_name=paste(figs.dir,"coef_diff_cdf_base","_",exercise,"_",save.ext,".png",sep = "")
png(figure_name)
ggplot(results.exercise, aes(coef_diff)) + stat_ecdf(geom = "step")
dev.off()

figure_name=paste(figs.dir,"obw_diff_cdf_base","_",exercise,"_",save.ext,".png",sep = "")
png(figure_name)
ggplot(results.exercise, aes(obw_diff)) + stat_ecdf(geom = "step")
dev.off()

```

### Correlation between baseline OBW and change in OBW
```{r correlation_obw}
cor(results$obw,results.exercise$obw_diff)
```

### Correlation between baseline coefficients and change in coefficients
```{r correlation_coef}
cor(results$coef,results.exercise$coef_diff)
```

### Summary results - table:
Note: coefficient (treatment effects) are normalized to zero, by subtracting from each estimate the size of the jump at the cutoff.
```{r table, echo=F}
results_table=as.data.frame(matrix(0, ncol = 3, nrow = 0))
results_table[1,1]=round(mean(results$coef),digits = 4)
results_table[1,2]=round(mean(results.exercise$coef),digits = 4)
results_table[1,3]=round(mean(results.exercise$coef_diff),digits = 4)
results_table[2,1]=round(mean(results$obw),digits = 4)
results_table[2,2]=round(mean(results.exercise$obw),digits = 4)
results_table[2,3]=round(mean(results.exercise$obw_diff),digits = 4)
colnames(results_table) = c("base",exercise,"diff_base")
rownames(results_table) = c("coef","obw")
kable(results_table, caption = "Summary Table")
```

### Interpreting results
`r ifelse(exercise=="zero","When replacing values outside OBW with zeros, the new OBW are smaller, but the estimated coefficients remain unbiased","When dropping values outside OBW, the new OBW are smaller, and the estimated coefficients are biased downwards")`


