---
title: "RD Robustness Project"
subtitle: "Exercise: dropping data away from cutoff"
author: "Maor Milgrom"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    df_print: paged
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, fig.height=4.5, root.dir = 'C:/Users/yaela/Dropbox (Brown)/Brown/RA/RD/R')
setwd("C:/Users/yaela/Dropbox (Brown)/Brown/RA/RD/R")  
```


# Introduction
The goal of this project is to test the robustness of the Regression-Discontinuity analysis to different extreme cases, via simulations, using the 'rdrobust' package.  

## This Document: Excercise \#3
Testing whether the RD coefficient becomes biased when we gradually drop observations in different intervals around the cutoff.


```{r packages, include=F}
library(dplyr)
library(rdrobust)
library(ggplot2)
library(reshape2)
library(knitr)
set.seed(1)
```

### Set Parameters
Here we set the main parameters for the excercise:

```{r parameters}
jump=10           # Size of jump at cutoff
loop=1000
figs.iter.save=5
quadratic=T       # T - quadratic DGP, F - linear
symm_obw="mserd"  # mserd - symmetric OBW, msetwo - asymmetric OBW 
normal.x=T        # T - normal draws of x around cutoff, F - uniform draws
dgp.sd=10         # sd of normal noise added to DGP
bc=F              # bias-corrected (bc) estimates or conventional (c)
intervals=c(5,10,20,40)
var.list=c("coef.c","coef.bc","obw.c","obw.bc")
```

```{r setup, include=F}
### dataframes for storing results
df.temp=as.data.frame(matrix(0, ncol = length(intervals), nrow = loop))
colnames(df.temp) = paste("int",intervals,sep="_")

for (df.name in var.list) {
  assign(df.name,df.temp)
}

### Extensions for files based on parameters selected
figs.dir="C:/Users/yaela/Dropbox (Brown)/Brown/RA/RD/R/figures/"
quad_test=ifelse(quadratic==T,"quadratic","linear")
normal_test=ifelse(normal.x==T,"rnorm","runif")
bc_test=ifelse(bc==T,"bc","c")
save.ext=paste(bc_test,quad_test,normal_test,sep = "_")
file.var=paste("summary_",save.ext,".html",sep = "")
begin.figures=loop-figs.iter.save
```


### Simulate DGP and plot
```{r dgp}
df <- as.data.frame(matrix(0, ncol = 0, nrow = length(seq(-100,100,0.01))))
df$x=round(seq(-100,100,0.01), digits=2)
df=subset(df,df$x!=0)
df$treated <- ifelse(df$x>0, 1, 0)

df$y.model<- 0.5*df$x  - 0.025*df$x^2*quadratic + jump*df$treated
df$y=df$y.model+rnorm(length(df$x),0,dgp.sd)

## dataframe for draws (samples)
sample.x <- as.data.frame(matrix(0, ncol = 0, nrow = nrow(df)/10))
```

```{r plot_dgp, echo=F}
df %>%
  filter(x > -50 & x < 50) %T>%
  plot(y~x,., ylim = range(c(y,y.model)),
       col="blue", ylab = "Y", xlab = "X") %T>%
  par(new = T) %>%
  plot(y.model~x,., ylim = range(c(y,y.model)),
       axes = FALSE, xlab = "", ylab = "")
  title(main = "DGP + Model")
```


### Iterations
Running `r loop` iterations, and presenting figures from last iteration for illustration
In each iteration, and for each of the `r length(intervals)` intervals, , we: \newline

1. Draw randomly `r nrow(df)/10` observations around the cutoff.
2. Keep data in that interval around cutoff
4. compute OBW and RD coefficient

```{r iterations, include=F}
for (i in 1:loop) {
  if (normal.x==T) {
    sample.x$x <- round(rnorm(nrow(df)/10, 0, 10),digits = 2) 
  } else {
    sample.x$x <- round(runif(nrow(df)/10, -20,20),digits = 2) 
  }

  sample.x=subset(sample.x, x>-100 & x<100)
  sample=as.data.frame(inner_join(df, sample.x, by="x"))

  for (j in intervals) {
    t=which(j==intervals)
    sample.int=subset(sample,x> -j & x< j)
     results.current=rdrobust(sample.int$y,sample.int$x, bwselect = symm_obw)
    coef.c[i,t]=results.current$coef[1]-jump
    coef.bc[i,t]=results.current$coef[2]-jump
    obw.c[i,t]=results.current$bws[1,1]
    obw.bc[i,t]=results.current$bws[2,1]
    
      if (i==1000) {
      sample.int %T>%
          plot(y~x,., ylim = range(c(y,y.model)),
             col="blue", ylab = "Y", xlab = "X") %T>%
        par(new = T) %>%
        plot(y.model~x,., ylim = range(c(y,y.model)),
             axes = FALSE, xlab = "", ylab = "")
      title(main = paste0("sample - interval of ",j))
    }
    }  
  }
```

## Results

### Figures summarizing iterations
```{r figures_summary_print, echo=F, fig.height=3}
fig.df <- data.frame(coef_bc=c(coef.bc$int_5,coef.bc$int_10,coef.bc$int_20,coef.bc$int_40), spec = rep(c("interval=5", "interval=10", "interval=20","interval=40"),
                                      each = loop))
fig.df$spec <- factor(fig.df$spec, levels =c("interval=5", "interval=10", "interval=20","interval=40"))
ggplot(fig.df, aes(x = coef_bc, fill = spec)) + geom_density(alpha = 0.3) +
  geom_vline(xintercept=0,  linetype="dashed") +
  labs(title = "Density of RD coefficients for different intervals",
       subtitle = "Bias-corrected estimates")
  
fig.df <- data.frame(coef_c=c(coef.c$int_5,coef.c$int_10,coef.c$int_20,coef.c$int_40), 
                  spec = rep(c("interval=5", "interval=10", "interval=20","interval=40"),                                                                                                    each = loop))
fig.df$spec <- factor(fig.df$spec, levels =c("interval=5", "interval=10", "interval=20","interval=40"))
ggplot(fig.df, aes(x = coef_c, fill = spec)) + geom_density(alpha = 0.3) +
  geom_vline(xintercept=0,  linetype="dashed") +
  labs(title = "Density of RD coefficients for different intervals",
       subtitle = "Conventional estimates")
```


```{r figures_summary_save, include=F}
fig.df <- data.frame(coef_bc=c(coef.bc$int_5,coef.bc$int_10,coef.bc$int_20,coef.bc$int_40), spec = rep(c("interval=5", "interval=10", "interval=20","interval=40"),
                                      each = loop))
fig.df$spec <- factor(fig.df$spec, levels =c("interval=5", "interval=10", "interval=20","interval=40"))
figure_name=paste(figs.dir,"coef_bc_interval_bias_",save.ext,".png",sep = "")

png(figure_name)
ggplot(fig.df, aes(x = coef_bc, fill = spec)) + geom_density(alpha = 0.3) +
  geom_vline(xintercept=0,  linetype="dashed")
dev.off()

fig.df <- data.frame(coef_c=c(coef.c$int_5,coef.c$int_10,coef.c$int_20,coef.c$int_40), 
                  spec = rep(c("interval=5", "interval=10", "interval=20","interval=40"),                                                                                                    each = loop))
fig.df$spec <- factor(fig.df$spec, levels =c("interval=5", "interval=10", "interval=20","interval=40"))
figure_name=paste(figs.dir,"coef_c_interval_bias_",save.ext,".png",sep = "")
png(figure_name)
ggplot(fig.df, aes(x = coef_c, fill = spec)) + geom_density(alpha = 0.3) +
  geom_vline(xintercept=0,  linetype="dashed")
dev.off()
```

### Summary results - Table 
Note: coefficients (treatment effects) are normalized to zero, by subtracting from each estimate the size of the jump at the cutoff.
```{r table, echo=F}
  results_table=as.data.frame(matrix(0, ncol = 4, nrow = 0))
  results_table[1,]=round(colMeans(coef.c),digits = 4)
  results_table[2,]=round(colMeans(coef.bc),digits = 4)
  results_table[3,]=round(colMeans(obw.c),digits = 4)
  results_table[4,]=round(colMeans(obw.bc),digits = 4)
  colnames(results_table) = paste("int",intervals,sep="_")
  rownames(results_table) =var.list
  kable(results_table, caption = "Summary Table")
```

### Interpreting results
We find that as we restrict the analysis to smaller intervals around the cutoff, not only the optimal OBW chosen is smaller, but the coefficients become biased downwards. 
