
---
title: "RD Project Summary"
author: "Maor Milgrom"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    df_print: paged
---

[//]: # knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding=encoding, output_file='new_file_name.html') })
[//]: # knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding=encoding, clean = FALSE) })

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, fig.width=6, fig.height=5, root.dir = 'C:/Users/yaela/Dropbox (Brown)/Brown/RA/RD/R')
```


# Introduction
The goal of this exercise is to try to test the robustnes of the Regression-Discontinuity analysis to different extreme cases, via simulations, using the 'rdrobust' package.  


## This Document: Excercise \#1
Replacing observations outside Optimal Bandwitdh (OBW) with zeros, or dropping them    


```{r packages, include=F}
#rmarkdown::render("simulations_baseline.Rmd", clean = FALSE) ???
rm(list=ls(all=TRUE))
library(dplyr)
library(rdrobust)
library(ggplot2)
library(reshape2)
#library(gridExtra)
library(knitr)
set.seed(1)
#library(kableExtra)
```


### Set Parameters
Here we set the main parameters for the excercise:

```{r parameters}
jump=10           # Size of jump at cutoff
loop=1000
figs.iter.save=5
quadratic=T       # T - quadratic DGP, F - linear
symm_obw="mserd"  # mserd - symmetric OBW, msetwo - asymmetric OBW 
normal.x=T        # T - normal draws of x around cutoff, F - uniform draws
dgp.sd=10         # sd of normal noise added to DGP
bc=F              # bias-corrected estimates or conventional
treat="zero"      # Type of exercise - "zero" or "bwo" ('bandwidth only')
```


```{r extensions, include=F}
### Extensions for files based on parameters selected
figs.dir="C:/Users/yaela/Dropbox (Brown)/Brown/RA/RD/R/figures/"
quad_test=ifelse(quadratic==T,"quadratic","linear")
normal_test=ifelse(normal.x==T,"rnorm","runif")
bc_test=ifelse(bc==T,"bc","c")
save.ext=paste(bc_test,quad_test,normal_test,sep = "_")
file.var=paste("summary_",save.ext,".html",sep = "")
begin.figures=loop-figs.iter.save
```



### Constructing dataframes for simulation and for results
```{r setup_df}
df <- as.data.frame(matrix(0, ncol = 0, nrow = length(seq(-100,100,0.01))))
df$x=round(seq(-100,100,0.01), digits=2)
df=subset(df,df$x!=0)
df$treated <- ifelse(df$x>0, 1, 0)
sample.x <- as.data.frame(matrix(0, ncol = 0, nrow = nrow(df)/10))

results<- as.data.frame(matrix(0, ncol = 4, nrow = loop))
colnames(results) <- c("coef","obw","obw_l","obw_r")
results.treat<- as.data.frame(matrix(0, ncol = 6, nrow = loop))
colnames(results.treat) <- c("coef","obw","obw_l","obw_r",
                             "coef_diff","obw_diff")
```


### Simulate DGP and plot
```{r dgp}
df$y.model<- 0.5*df$x  - 0.025*df$x^2*quadratic + jump*df$treated
df$y=df$y.model+rnorm(length(df$x),0,dgp.sd)

df %>%
  filter(x > -50 & x < 50) %T>%
  plot(y~x,., ylim = range(c(y,y.model)),
       col="blue", ylab = "Y", xlab = "X") %T>%
  par(new = T) %>%
  plot(y.model~x,., ylim = range(c(y,y.model)),
       axes = FALSE, xlab = "", ylab = "")
  title(main = "DGP + Model")

```


```{r dgp_plot_save, include=FALSE}
figure_name=paste(figs.dir,"dgp_",quad_test,".png",sep = "")
png(figure_name)
df %T>%
  plot(y~x,., ylim = range(c(y,y.model)),
       col="blue", ylab = "Y", xlab = "X") %T>%
  par(new = T) %>%
  plot(y.model~x,., ylim = range(c(y,y.model)),
       axes = FALSE, xlab = "", ylab = "")
dev.off()

```

### Iterations
Running `r loop` iterations, and saving figures from `r figs.iter.save` last iterations to file
```{r iterations, results = 'hide'}
for(i in 1:loop) {
  if (normal.x==T) {
    sample.x$x <- round(rnorm(nrow(df)/10, 0, 10),digits = 2) 
  } else {
    sample.x$x <- round(runif(nrow(df)/10, -20,20),digits = 2) 
  }
  
  sample.x=subset(sample.x, x>-100 & x<100)
  sample=as.data.frame(inner_join(df, sample.x, by="x"))
  results.current=rdrobust(sample$y,sample$x,bwselect = symm_obw)
  results[i,1]=results.current$coef[bc+1]-jump # normalizing to zero
  results[i,3:4]=results.current$bws[bc+1,1:2]
  results[i,2]=results[i,3]+results[i,4]
  

  if (treat=="zero") {
    sample.treat=sample
    sample.treat$y <- ifelse(sample$x> -results[i,3] & 
                                     sample$x< results[i,4], sample$y, 0)
    
  } else if (treat=="bwo") {
    sample.treat=subset(sample,x> -results[i,3] & x< results[i,4])
  }
  
  results.current=rdrobust(sample.treat$y,sample.treat$x)
  results.treat[i,1]=results.current$coef[bc+1]-jump # normalizing to zero
  results.treat[i,3:4]=results.current$bws[bc+1,1:2]
  results.treat[i,2]=results.treat[i,3]+results.treat[i,4]
  
  results.treat[i,5:6]=results[i,1:2]-results.treat[i,1:2] # computing diff from base

if (i >= begin.figures) {
    coef_base=paste("Base: Coef = ",round(results[i,1],digits = 2)+jump,sep = "")
    coef_treat=paste(treat,": Coef = ",round(results.treat[i,1],digits = 2)+jump,sep = "")
    
    figure_name=paste(figs.dir,"sample",i,treat,"_",save.ext,"_","model.png",sep = "")
    png(figure_name)
    temp.treat=sample.treat %>%
      filter(x > -20 & x < 20)
    temp=sample %>%
      filter(x > -20 & x < 20)
    plot(temp$y~temp$x, ylim = range(c(temp.treat$y,temp$y)),
         xlim = range(c(temp.treat$x,temp$x)),
         col="red", ylab = "Y", xlab = "X")
    par(new = T)
    plot(temp.treat$y~temp.treat$x, ylim = range(c(temp.treat$y,temp$y)),
         xlim = range(c(temp.treat$x,temp$x)),
         col="blue", ylab = "Y", xlab = "X")
    par(new = T)
    plot(temp$y.model~temp$x, ylim = range(c(temp.treat$y,temp$y)),
         xlim = range(c(temp.treat$x,temp$x)),
         col="black", ylab = "Y", xlab = "X")
    abline(v = c(-results[i,3], -results.treat[i,3],
                 results[i,4], results.treat[i,4]),
           col=c("blue","red", "blue", "red"),
           lty=c(1,2,1,2), lwd=c(1,2,1,2))
    legend("top", legend=c(coef_base, coef_treat),
           col=c("blue", "red"), lty=1:2, cex=0.8)
    dev.off()
    
    
    figure_name=paste(figs.dir,"rd_plot",i,"_",save.ext,".png",sep = "")
    png(figure_name)
    rdplot(sample$y,sample$x)
    dev.off()
    
    
    figure_name=paste(figs.dir,"sample",i,"_",save.ext,".png",sep = "")
    png(figure_name)
    sample %>%
      filter(x > -30 & x < 30) %T>%
      plot(y~x,., ylim = range(c(y,y.model)),
           col="blue", ylab = "Y", xlab = "X") %T>%
      par(new = T) %>%
      plot(y.model~x,., ylim = range(c(y,y.model)),
           axes = FALSE, xlab = "", ylab = "")
    dev.off()
  }
}
#data_name=paste("base_data","_",treat,"_",save.ext,".RData",sep = "")
#save.image(data_name)

```


### Presenting figures from last iteration for illustration

```{r sample_figures_present}
    i=loop
    coef_base=paste("Base: Coef = ",round(results[i,1],digits = 2)+jump,sep = "")
    coef_treat=paste(treat,": Coef = ",round(results.treat[i,1],digits = 2)+jump,sep = "")
    
      sample %>%
      filter(x > -30 & x < 30) %T>%
      plot(y~x,., ylim = range(c(y,y.model)),
           col="blue", ylab = "Y", xlab = "X") %T>%
      par(new = T) %>%
      plot(y.model~x,., ylim = range(c(y,y.model)),
           axes = FALSE, xlab = "", ylab = "")
      title(main = "Draw from DGP + Model")
    
    rdplot(sample$y,sample$x, title = "RD Plot for basline")

    temp.treat=sample.treat %>%
      filter(x > -20 & x < 20)
    temp=sample %>%
      filter(x > -20 & x < 20)
    plot(temp$y~temp$x, ylim = range(c(temp.treat$y,temp$y)),
         xlim = range(c(temp.treat$x,temp$x)),
         col="red", ylab = "Y", xlab = "X")
    par(new = T)
    plot(temp.treat$y~temp.treat$x, ylim = range(c(temp.treat$y,temp$y)),
         xlim = range(c(temp.treat$x,temp$x)),
         col="blue", ylab = "Y", xlab = "X")
    par(new = T)
    plot(temp$y.model~temp$x, ylim = range(c(temp.treat$y,temp$y)),
         xlim = range(c(temp.treat$x,temp$x)),
         col="black", ylab = "Y", xlab = "X")
    abline(v = c(-results[i,3], -results.treat[i,3],
                 results[i,4], results.treat[i,4]),
           col=c("blue","red", "blue", "red"),
           lty=c(1,2,1,2), lwd=c(1,2,1,2))
    legend("topleft", legend=c(coef_base, coef_treat),
           col=c("blue", "red"), lty=1:2, cex=0.8)
    title(main = paste0("Comparing baseline to ",treat))
    
    
    rdplot(sample.treat$y,sample.treat$x, title = paste0("RD Plot for ",treat))
```


## Results

### Figures summarizing iterations
```{r figures_summary_print}

## PDF'S OF LEVELS
ggplot(results, aes(coef)) +  stat_density(geom="line") + 
  geom_vline(aes(xintercept=0), colour="#BB0000", linetype="dashed") +
  ggtitle("Density of RD coefficients: basline")


ggplot(results.treat, aes(coef)) + stat_density(geom="line") +
  geom_vline(aes(xintercept=0), colour="#BB0000", linetype="dashed") +
    ggtitle(paste0("Density of RD coefficients: ",treat))


### treat_base_diff
ggplot(results.treat, aes(coef_diff)) + stat_ecdf(geom = "step") +
      ggtitle(paste0("CDF of difference b/w coefficients of baseline and ",treat))


ggplot(results.treat, aes(obw_diff)) + stat_ecdf(geom = "step") +
        ggtitle(paste0("CDF of difference b/w OBW of baseline and ",treat))

```

```{r figures_summary_save, include=F}

## PDF'S OF LEVELS
figure_name=paste(figs.dir,"coef","_",save.ext,".png",sep = "")
png(figure_name)
ggplot(results, aes(coef)) + stat_density(geom="line") + 
  geom_vline(aes(xintercept=0), colour="#BB0000", linetype="dashed")
dev.off()


figure_name=paste(figs.dir,"coef","_",treat,"_",save.ext,".png",sep = "")
png(figure_name)
ggplot(results.treat, aes(coef)) + stat_density(geom="line") +
  geom_vline(aes(xintercept=0), colour="#BB0000", linetype="dashed")
dev.off()


### treat_base_diff
figure_name=paste(figs.dir,"coef_diff_cdf_base","_",treat,"_",save.ext,".png",sep = "")
png(figure_name)
ggplot(results.treat, aes(coef_diff)) + stat_ecdf(geom = "step")
dev.off()

figure_name=paste(figs.dir,"obw_diff_cdf_base","_",treat,"_",save.ext,".png",sep = "")
png(figure_name)
ggplot(results.treat, aes(obw_diff)) + stat_ecdf(geom = "step")
dev.off()

```

### Correlation between baseline OBW and difference in OBW
```{r correlation_obw}
cor(results$obw,results.treat$obw_diff)
```

### Correlation between baseline coefficients and difference in coefficients
```{r correlation_coef}
cor(results$coef,results.treat$coef_diff)
```

### Summary results - TABLE 
```{r table}
results_table=as.data.frame(matrix(0, ncol = 3, nrow = 0))
results_table[1,1]=round(mean(results$coef),digits = 4)
results_table[1,2]=round(mean(results.treat$coef),digits = 4)
results_table[1,3]=round(mean(results.treat$coef_diff),digits = 4)
results_table[2,1]=round(mean(results$obw),digits = 4)
results_table[2,2]=round(mean(results.treat$obw),digits = 4)
results_table[2,3]=round(mean(results.treat$obw_diff),digits = 4)
colnames(results_table) = c("base",treat,"diff_base")
rownames(results_table) = c("coef","obw")
kable(results_table, caption = "Summary Table")
```




